\newpage
\section{Introduction}
Defining good threat models can be very helpful in improving existing systems, or contribute in building of better, safer and more fault tolerant systems.
Threat models are especially important in Software engineering and Computer Science in general because it is a relatively new field of research.
A threat model can help us to understand how a particular system reacts to a situation that is different from normal operating conditions.
The limits that a threat model imposes makes it easier to discuss and reach conclusions in a predefined scenario.

In this paper, the threat models are picked up in that way so they can be used to compare the ability of the centralised and decentralised computer systems to deal with circumstances other than normal.
The focus has been narrowed down to the centralized and decentralized computer networks, as they are typical examples of centralized and decentralized systems. Also applications that rely on specific network architecture will be used in our work.
The most popular applications among the users now are the social networking sites. The absolute giant among them is Facebook, which has recently passed one billion users \cite{web:facebookpassesbillion}. Other popular social networks are Twitter, Google Plus, MySpace, LinkedIn.
Conclusions for decentralised computer systems will be made after observing how threat models affect peer-to-peer networks.
The whole set of decentralised networks has been reduced to just peer-to-peer networks, because they have the essential characteristics that are of interest.
Also there is whole class of applications between centralised and decentralised model like e-mail, DNS and XMPP that have both centralised and decentralised characteristics.
They are not subject of interest in this paper.

The figures of Internet penetration \cite{web:internetworldstats} in human societies, implies that people need these tools even in the most harsh conditions.
Especially important are problems which can occur in the infrastructure of the computer systems or threats related to security.
In the security threats, special emphasis has been put on user's data.
Threat models have been modelled to target both of the mentioned aspects of potential flaws.
The most important thing is that this paper does not capture the whole picture of a threat, but rather than that certain characteristics had been taken to model the newly occurred situation.

The rest of the paper is structured as follows.
In Section 2 the research methods to produce this paper along with the methods for building the threat models have been presented.
Next, in the Section 3 there is a short summary of all three threat models.
In the Sections 4, 5 and 6 respectively, the previously defined threat models have been applied on both centralised and decentralised computer systems.
The predicted reactions of the systems under the new conditions are used in the Section 7 where the conclusion is presented based on the previous findings.
